stats-project

### 2020-12-03 R - Deliverable/MSDS 6371 - Project.Rmd
Fix Variable name
Initial Commit

```{r message=FALSE, warning=FALSE}
library(olsrr)
library(tidyverse)
library(ggpubr)
library(ggplot2)
library(car)
library(data.table)
library(mltools)
library(olsrr)

@@

```{r message=FALSE, warning=FALSE}
data_train= read_csv("../Data/train.csv")
data_test = read_csv("../Data/test.csv")
#Convert <chr> to <fctr>
data_train = as.data.frame(unclass(data_train))
data_test = as.data.frame(unclass(data_test))
nrow(data_test)
```

@@

summary(lm_fit_experiment)
#confint(lm_fit_experiment,  level=0.995)

@@

```{r message=FALSE, warning=FALSE}
for (i in unlist(unique(data$Neighborhood)) ) {
  print(scatter_func(data, i))
}

@@

#Reference Neighborhood_BrkSide
lm_fit_q1 = lm(SalePrice ~. -Id-Neighborhood_BrkSide+Neighborhood_Edwards*GrLivArea+Neighborhood_NAmes*GrLivArea, data = one_encode_train_data_q1)

>>>>

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(ggpubr)
library(ggplot2)
library(car)
library(data.table)
library(mltools)
library(olsrr)

@@

```{r message=FALSE, warning=FALSE}
data_train= read_csv("../Data/train.csv")
data_test = read_csv("../Data/test.csv")
#Convert <chr> to <fctr>
data_train = as.data.frame(unclass(data_train))
data_train$Neighborhood = as.factor(data_train$Neighborhood )
data_test = as.data.frame(unclass(data_test))
data_test$Neighborhood = as.factor(data_test$Neighborhood )
head(data_train)
```

@@

#summary(lm_fit_experiment)
#confint(lm_fit_experiment,  level=0.995)

@@

```{r message=FALSE, warning=FALSE}
for (i in unlist(unique(data_train$Neighborhood)) ) {
  print(scatter_func(data_train, i))
}

@@

#Reference Neighborhood_BrkSide
lm_fit_q1 = lm(SalePrice ~-Id- Neighborhood_BrkSide+ GrLivArea+Neighborhood_Edwards+Neighborhood_NAmes+ Neighborhood_Edwards*GrLivArea+Neighborhood_NAmes*GrLivArea, data = one_encode_train_data_q1)
